---
title: "SimulateRT_LBA"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Simulate RTs with a hierarchical LBA model (2stim x 2CohLevels x 2AngleLevels)

We use DMC for the Bayesian fitting of the hierarchical model. First thing first we need to invoke the model from DMC. DMC requires to set the working directory on its folder. Once loaded the model we can go back to our working directory and load the required libraries.

```{r cars, message=FALSE, warning=FALSE}
wd <- here::here();

setwd("/Users/ale/ownCloud/3-R/DMC_190819/")
source("dmc/dmc.R")
load_model (dir_name="LBA",model_name="lba_B.R")

setwd(wd)

set.seed(123)#for reproducibility

pacman::p_load('tidyverse','magrittr')

```

# Set up the model

1- Define the factorial design: 2 motion directions x 2 coherence levels x 2 angles \* s1/s2 left and right motion direction \* cohE/cohH easy/hard coherence \* angleE/angleH easy/hard angle

2 - Create "match.map", a list of lists, where the first entry is a list named "M" that specifies which accumulator matches the correct response for each factor level. Accumulators can be specified by the corresponding response name or an integer 1..n for n response possibilities

3 - Create "const", a vector which specifies the parameters to be held constant (i.e., not varied in fitting), and their values. In order to identify the model, the moment-to-moment variability of the accumulation rate is fixed to one, consitent with Sigmann et al., 2017.

```{r}
factors <- list(S=c("s1","s2"),Coh=c("cohE","cohH"),Angle=c("angleE","angleH"))
responses <- c("r1","r2") # keys o and p

match.map <- list(M=list(s1="r1",s2="r2"))

const <- c(sd_v.false=1,st0=0)
```

# Generate model1: manipulations affect decision boundary

-   Create "p.map", a list where the above specified factors are mapped onto the parameters of the model
-   Generate model1

```{r}
# boundary  changes with manipulations, accum-rate faster for correct
p.map <- list(A="1",B=c("Coh","Angle"),t0="1",mean_v=c("M"),sd_v="M",st0="1")

model1 <- model.dmc(p.map,match.map = match.map,constants=const,
                   responses=responses,factors=factors)

```

# Simulate RTs from model1

Each subject can be thought of as a random effect. That is, rather than thinking of each subject as being completely unrelated to all other subjects we treat them as coming from the same population. In practice this means that each subject's parameters are from a population distribution. This can be done with the "p.prior" (parameter prior) argument toh.simulate.dmc where the prior.p.dmc function defines distributions from which parameters can be sampled. We will use the default distribution (normal), requiring a mean (p1) and standard deviation (p2) parameter. Here we use p.vector to give the means and the same sd for all parameters (a vector for p2 allows different sds for each parameter).

```{r}
pop.mean <- c(A=0.5, B.cohE.angleE = 3, B.cohE.angleH = 4, B.cohH.angleE = 5,
              B.cohH.angleH=6,mean_v.true=2,mean_v.false=-1,
              sd_v.true=0.5, t0=.2)

pop.scale <-c(A=.1, B.cohE.angleE = .1, B.cohE.angleH = .1, B.cohH.angleE = .1, 
              B.cohH.angleH = .1,mean_v.true=.2,mean_v.false=.2,
              sd_v.true=0.1,t0=.05)

pop.prior <- prior.p.dmc(
  dists = rep("tnorm",9),
  p1=pop.mean,p2=pop.scale,
  lower=c(0,0,0,0,0,NA,NA,0,.1),upper=c(NA,NA,NA,NA,NA,NA,NA,NA,1)
)

##  Check population distributions
par(mfcol=c(2,5)); for (i in names(pop.prior)) plot.prior(i,pop.prior)
```

Simulate data: ns subjects, with n data point per design cell

```{r}
raw.data1 <- h.simulate.dmc(model1, p.prior = pop.prior, n = 150, ns = 20)
data.model1 <- data.model.dmc(raw.data1, model1)

# Take a look at parameters
ps <- round( attr(raw.data1, "parameters"), 2)
round(apply(ps,2,mean),2)
```

Plot data from a subject:

First column=response left, Rows = EasyCoh-EasyAngle, EasyCoh-HardAngle,HardCoh-EasyAngle, HardCoh-HardAngle

```{r}

par(mfcol=c(1,4)) 
for (i in 1) { # First column=response left, Second column = response right. Rows = EasyCoh-EasyAngle, EasyCoh-HardAngle,HardCoh-EasyAngle, hard-hard
  plot.cell.density(data.cell=data.model1[[i]][data.model1[[i]]$Coh=="cohE" & data.model1[[i]]$Angle=="angleE" & data.model1[[i]]$S=="s1",],C="r1",xlim=c(1,6),show.mean = TRUE)
  plot.cell.density(data.cell=data.model1[[i]][data.model1[[i]]$Coh=="cohE" & data.model1[[i]]$Angle=="angleH" & data.model1[[i]]$S=="s1",],C="r1",xlim=c(1,6),show.mean = TRUE)
  plot.cell.density(data.cell=data.model1[[i]][data.model1[[i]]$Coh=="cohH" & data.model1[[i]]$Angle=="angleE" & data.model1[[i]]$S=="s1",],C="r1",xlim=c(1,6),show.mean = TRUE)
  plot.cell.density(data.cell=data.model1[[i]][data.model1[[i]]$Coh=="cohH" & data.model1[[i]]$Angle=="angleH" & data.model1[[i]]$S=="s1",],C="r1",xlim=c(1,6),show.mean = TRUE)

  # plot.cell.density(data.cell=data.model1[[i]][data.model1[[i]]$Coh=="cohE" & data.model1[[i]]$Angle=="angleE" & data.model1[[i]]$S=="s2",],C="r2",xlim=c(1,6),show.mean = TRUE)
  # plot.cell.density(data.cell=data.model1[[i]][data.model1[[i]]$Coh=="cohE" & data.model1[[i]]$Angle=="angleH" & data.model1[[i]]$S=="s2",],C="r2",xlim=c(1,6),show.mean = TRUE)
  # plot.cell.density(data.cell=data.model1[[i]][data.model1[[i]]$Coh=="cohH" & data.model1[[i]]$Angle=="angleE" & data.model1[[i]]$S=="s2",],C="r2",xlim=c(1,6),show.mean = TRUE)
  # plot.cell.density(data.cell=data.model1[[i]][data.model1[[i]]$Coh=="cohH" & data.model1[[i]]$Angle=="angleH" & data.model1[[i]]$S=="s2",],C="r2",xlim=c(1,6),show.mean = TRUE)
  
}  
```

# Generate model2: manipulations affect accumulation-rate

-   Create "p.map", a list where the above specified factors are mapped onto the parameters of the model
-   Generate model1

```{r}
# accumulation rate  changes with manipulations and correct responses
p.map <- list(A="1",B= "1",t0="1",mean_v=c("Coh","Angle","M"),sd_v="M",st0="1")

model2 <- model.dmc(p.map,match.map = match.map,constants=const,
                    responses=responses,factors=factors)

```

# Simulate RTs from model2

We will use the default distribution (normal), requiring a mean (p1) and standard deviation (p2) parameter. Here we use p.vector to give the means and the same sd for all parameters (a vector for p2 allows different sds for each parameter).

```{r}
# Population distribution, Coherence and Angle effect on accumulation rate

pop.mean <- c(A=0.5, B = 3,  mean_v.cohE.angleE.true = 3, mean_v.cohE.angleH.true = 2.5,
              mean_v.cohH.angleE.true = 2.5, mean_v.cohH.angleH.true = 2,
              mean_v.cohE.angleE.false = 0, mean_v.cohE.angleH.false = 0, 
              mean_v.cohH.angleE.false = 0, mean_v.cohH.angleH.false = 0,
              sd_v.true=0.5,t0=.2)


pop.scale <-c(A=.1, B = .1,  mean_v.cohE.angleE.true = .2, mean_v.cohE.angleH.true = .2,
              mean_v.cohH.angleE.true = .2, mean_v.cohH.angleH.true = .2,
              mean_v.cohE.angleE.false = .2, mean_v.cohE.angleH.false = .2, 
              mean_v.cohH.angleE.false = .2, mean_v.cohH.angleH.false = .2, 
              sd_v.true=0.1, t0=.05)

check.p.vector(pop.mean,model2)
check.p.vector(pop.scale,model2)



pop.prior <- prior.p.dmc(
  dists = rep("tnorm",12),
  p1=pop.mean,p2=pop.scale,
  lower=c(0,0,NA,NA,NA,NA,NA,NA,NA,NA,0,.1),upper=c(NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,1)
)

##  Check population distributions
par(mfcol=c(2,6)); for (i in names(pop.prior)) plot.prior(i,pop.prior)
```

Simulate data: ns subjects, with n data point per design cell

```{r}
# Simulate some data
raw.data2 <- h.simulate.dmc(model2, p.prior = pop.prior, n = 150, ns = 20)
data.model2 <- data.model.dmc(raw.data2, model2)

# Take a look at parameters
ps <- round( attr(raw.data2, "parameters"), 2)
round(apply(ps,2,mean),2)
```

Plot data from a subject:

First column=response left, Rows = EasyCoh-EasyAngle, EasyCoh-HardAngle,HardCoh-EasyAngle, HardCoh-HardAngle

```{r}

# Take a look at the first  subject's data
par(mfcol=c(1,4)) 
for (i in 1) { # First column=response left, Second column = response right. Rows = EasyCoh-EasyAngle, EasyCoh-HardAngle,HardCoh-EasyAngle, hard-hard
  plot.cell.density(data.cell=data.model2[[i]][data.model2[[i]]$Coh=="cohE" & data.model2[[i]]$Angle=="angleE" & data.model2[[i]]$S=="s1",],C="r1",xlim=c(1,6),show.mean = TRUE)
  plot.cell.density(data.cell=data.model2[[i]][data.model2[[i]]$Coh=="cohE" & data.model2[[i]]$Angle=="angleH" & data.model2[[i]]$S=="s1",],C="r1",xlim=c(1,6),show.mean = TRUE)
  plot.cell.density(data.cell=data.model2[[i]][data.model2[[i]]$Coh=="cohH" & data.model2[[i]]$Angle=="angleE" & data.model2[[i]]$S=="s1",],C="r1",xlim=c(1,6),show.mean = TRUE)
  plot.cell.density(data.cell=data.model2[[i]][data.model2[[i]]$Coh=="cohH" & data.model2[[i]]$Angle=="angleH" & data.model2[[i]]$S=="s1",],C="r1",xlim=c(1,6),show.mean = TRUE)
  
}  
```
